Associations between Chlorophyll *a* and various Microcystin-LR Health Advisory Concentrations

### 2015-06-01 manuscript/manuscript.Rmd
re rendered with asis on table

```{r mc_chla_table, echo=FALSE}
mc_chla_tbl <- data.frame(Source=mc_names,Microcystin=mc_guides,Chlorophyll=mc_chla)
pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
```

>>>>

```{r mc_chla_table, results='asis', echo=FALSE}
mc_chla_tbl <- data.frame(Source=mc_names,Microcystin=mc_guides,Chlorophyll=mc_chla)
pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
```
